Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2015-07-27 paper/main.tex
import limitations and edits from pldi

>>>>

\paraskip
\paragraph{Limitations.}
The implementation of our analysis does not currently support all of Clight.
Function pointers, goto statements, and stack-allocated
variables that have their address taken are not supported by the
automatic analysis.  While these limitations concern the current
implementation, our technique is in principle capable to handle them.

For the sake of simplicity, the automated system described here is
restricted to finding only linear bounds.  However, the amortized analysis
technique was shown to work with polynomial bounds~\cite{HoffmannAH11};
we leave this extension of our system as future work.

Even some linear programs cannot be analyzed automatically by
$\toolname$, it is usually the case for programs that rely on heap
invariants (like nul-terminated C strings), for programs making
use of non-linear operations (like \code{\%} or \code{*}), or for
programs whose
termination can only be proved by complex path-sensitive reasoning.
